---
title: "Polygon Tiling Examples"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Polygon Tiling Examples}
    %\VignetteEngine{knitr::rmarkdown}
    \usepackage[utf8]{inputenc}
---

### Table of Contents

[Uniform tilings](#uniform)

* [Triangular tiling](#triangle)
* [Square tiling](#square)
* [Hexagonal tiling](#hexagon)
* [Snub square tiling](#snubsquare)
* [Truncated square tiling](#truncatedsquare)
* [Truncated hexagonal tiling](#truncatedhex)
* [Trihexagonal tiling](#trihexagon)
* [Snub trihexagonal tiling](#snubtrihex)
* [Truncated trihexagonal tiling](#truncatedtrihexagon)
* [Rhombitrihexagonal tiling](#rhombitrihexagon)
* [Additional uniform tilings with star polygons](#star)

[Non-uniform tilings](#non)

* [Herringbone tiling](#herringbone)
* [Pythagorean tiling](#pythagorean)
* [Rhombille tiling](#rhombille)
* [Tetrakis square tiling](#tetrakis)
* [Additional tilings using rhombi](#rhombi)

Several [uniform regular polygon tiling patterns](https://en.wikipedia.org/wiki/Uniform_tiling) can be achieved by use of `grid.pattern_regular_polygon()` plus occasionally `grid.polygon()` to set a background color.  This vignette highlights several such tiling patterns plus a couple notable non-uniform tiling patterns.

```{r}
library("grid")
library("gridpattern")
add_borders <- function() {
    pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
    grid.rect(gp = gpar(fill = NA, col = "white", lwd = 6))
    popViewport()
    pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
    grid.rect(gp = gpar(fill = NA, col = "white", lwd = 6))
    popViewport()
    pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
    grid.rect(gp = gpar(fill = NA, col = "white", lwd = 6))
    popViewport()
    pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
    grid.rect(gp = gpar(fill = NA, col = "white", lwd = 6))
    popViewport()
}
x_sq <- c(0, 0, 1, 1)
y_sq <- c(0, 1, 1, 0)
# colorblind accessible scheme https://jfly.uni-koeln.de/color/
blue <- grDevices::rgb(0.35, 0.70, 0.90)
yellow <- grDevices::rgb(0.95, 0.90, 0.25)
red <- grDevices::rgb(0.80, 0.40, 0.00)
green <- grDevices::rgb(0.00, 0.60, 0.50)
orange <- grDevices::rgb(0.90, 0.60, 0.00)
```

<a name="uniform">Uniform tilings</a>
=====================================

<a name="triangle">Triangular tiling</a>
-----------------------------------------

When we consider the background to be a triangle fill color we can straight-forwardly
achieve several of the [uniform colorings of a triangular tiling](https://en.wikipedia.org/wiki/Triangular_tiling#Uniform_colorings) using the "convex3" shape with the "hex" grid.

```{r}
grid.triangular_tiling <- function(...) {
    grid.pattern_regular_polygon(..., shape = "convex3", density = 1, grid = "hex",
                                 spacing = 0.2, angle = 0, rot = 180)
}
# 1 color uniform triangular tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = yellow, col = "black")
grid.triangular_tiling(gp = gp)
popViewport()

# 2 color uniform triangular tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = red, col = "black")
grid.triangular_tiling(gp = gp)
popViewport()

# 3 color uniform triangular tiling
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = c(blue, red), col = "black")
grid.triangular_tiling(gp = gp)
popViewport()

# 4 color uniform triangular tiling
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = c(red, blue, green), col = "black")
grid.triangular_tiling(gp = gp)
popViewport()
add_borders()
```

<a name="square">Square tiling</a>
----------------------------------

We can achieve the nine non-staggered [uniform colorings of a square tiling](https://en.wikipedia.org/wiki/Square_tiling#Uniform_colorings) using the "square" shape and the appropriate "type" (and perhaps "subtype").

```{r}
# 2 color uniform square tiling (1212)
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = c(yellow, red), col = "black")
grid.pattern_regular_polygon(shape = "square", density = 1, 
                             spacing = 0.2, angle = 0, gp = gp)
popViewport()
# 2 color uniform square tiling (1122)
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = c(yellow, red), col = "black")
grid.pattern_regular_polygon(shape = "square", density = 1, type = "horizontal",
                             spacing = 0.2, angle = 0, gp = gp)
popViewport()
# 3 color uniform square tiling (1213)
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
gp <- gpar(fill = c(yellow, red, blue), col = "black")
grid.pattern_regular_polygon(shape = "square", density = 1,
                             spacing = 0.2, angle = 0, gp = gp)
popViewport()
# 4 color uniform square tiling (1234)
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
gp <- gpar(fill = c(yellow, red, blue, green), col = "black")
grid.pattern_regular_polygon(shape = "square", density = 1,
                             spacing = 0.2, angle = 0, gp = gp)
popViewport()
add_borders()
```

<a name="hexagon">Hexagonal tiling</a>
--------------------------------------------

We can achieve all the [uniform colorings of a hexagonal tiling](https://en.wikipedia.org/wiki/Hexagonal_tiling#Uniform_colorings) using the "convex6" shape with the "hex" grid and the appropriate "type".  Replacing the "convex6" shape with an appropriately scaled "star6" shape results in a uniform tiling using star polygons.

```{r}
grid.hexagonal_tiling <- function(..., shape = "convex6", spacing = 0.2) {
    scale <- star_scale(6, 30)
    grid.pattern_regular_polygon(..., shape = shape, density = 1, grid = "hex",
                                 spacing = spacing, scale = scale, angle = 0)
}
# 1 color uniform hexagonal tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = yellow, col = "black")
grid.hexagonal_tiling(gp = gp)
popViewport()

# One of several 2 color uniform hexagonal tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = c(red, yellow), col = "black")
grid.hexagonal_tiling(gp = gp)
popViewport()

# 3 color uniform hexagonal tiling
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
gp <- gpar(fill = c(yellow, red, blue), col = "black")
grid.hexagonal_tiling(gp = gp)
popViewport()

# (4.6_{π/6})^3
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = red, col = "black")
grid.hexagonal_tiling(shape = "star6", spacing = 0.3, gp = gp)
popViewport()
add_borders()
```

<a name=snubsquare>Snub square tiling</a>
-----------------------------------------

We can achieve the two [uniform colorings of a snub square tiling](https://en.wikipedia.org/wiki/Snub_square_tiling) using a "star4" shape and a "convex4" shape.

```{r}
grid.snub_square <- function(..., gp_sq, gp_sq2 = gp_sq, gp_tri = gp_sq) {
    scale_star <- star_scale(4, 90 + 60, external = TRUE)
    grid.polygon(x_sq, y_sq, gp = gp_sq)
    grid.pattern_regular_polygon(shape = "star4", scale = scale_star,
                                 angle = 0, rot = 15, spacing = 0.2,
                                 density = 1.4, gp = gp_tri)
    grid.pattern_regular_polygon(shape = "convex4", scale = scale_star,
                                 angle = 0, rot = 60, spacing = 0.2,
                                 density = scale_star * 1.4, gp = gp_sq2)
}

# 2 color uniform snub square tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
gp_y <- gpar(fill = yellow, col = "black")
gp_r <- gpar(fill = red, col = "black")
grid.snub_square(gp_sq = gp_y, gp_tri = gp_r)
popViewport()

# 3 color uniform snub square tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
gp_b <- gpar(fill = blue, col = "black")
grid.snub_square(gp_sq = gp_r, gp_sq2 = gp_b, gp_tri = gp_y)
popViewport()

# 1 color uniform hexagonal tiling
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.snub_square(gp_sq = gp_y)
popViewport()

pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
popViewport()
add_borders()
```

<a name=truncatedsquare>Truncated square tiling</a>
---------------------------------------------------

We can achieve the two [uniform colorings of a truncated square tiling](https://en.wikipedia.org/wiki/Truncated_square_tiling#Uniform_colorings) using the "convex8" shape rotated 22.5 degrees.  Adding in an extra (possibly alternating) "star8" shape results in a uniform tiling using star polygons.


```{r}
# 2 color uniform truncated square tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = red, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = yellow, col = "black")
grid.pattern_regular_polygon(shape = "convex8", density = 1.082, rot = 22.5, 
                             angle = 0, spacing = 0.3, gp = gp)
popViewport()

# 3 color uniform truncated square tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = blue, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = c(red, yellow), col = "black")
grid.pattern_regular_polygon(shape = "convex8", density = 1.082, rot = 22.5, 
                             angle = 0, spacing = 0.3, gp = gp)
popViewport()

# 3 color uniform truncated square tiling with star
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
gp <- gpar(fill = red, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = yellow, col = "black")
grid.pattern_regular_polygon(shape = "convex8", density = 1.082, rot = 22.5, 
                             angle = 0, spacing = 0.3, gp = gp)
gp <- gpar(fill = orange, col = "black")
scale <- star_scale(8, 60, external = TRUE)
grid.pattern_regular_polygon(shape = "star8", density = 1.082, rot = 22.5, 
                             angle = 0, scale = scale, spacing = 0.3, gp = gp)
popViewport()

# 4 color uniform truncated square tiling with an alternating star
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
gp <- gpar(fill = blue, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = c(red, yellow), col = "black")
grid.pattern_regular_polygon(shape = "convex8", density = 1.082, rot = 22.5, 
                             angle = 0, spacing = 0.3, gp = gp)
gp <- gpar(fill = orange, col = c("black"))
grid.pattern_regular_polygon(shape = c("null", "star8"), 
                             density = 1.082, rot = 22.5, 
                             angle = 0, scale = scale, spacing = 0.3, gp = gp)
popViewport()
add_borders()
```

<a name="truncatedhex">Truncated hexagonal tiling</a>
-----------------------------------------------------

We can achieve a [truncated hexagonal tiling](https://en.wikipedia.org/wiki/Truncated_hexagonal_tiling) using the "convex12" shape with a 15 degree rotation in a "hex_circle" grid.  The related "star12" variations are fun tilings as well.

```{r}
# 2 color uniform truncated hexagonal tiling
grid.truncated_hexagonal_tiling <- function(..., shape = "convex12") {
    scale <- star_scale(12, 60, external = TRUE)
    grid.pattern_regular_polygon(..., shape = shape, density = 1.034, spacing = 0.3,
                                 angle = 0, rot = 15, scale = scale, 
                                 grid = "hex_circle")
}
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = red, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = yellow, col = "black")
grid.truncated_hexagonal_tiling(gp = gp)
popViewport()

# Add in a "convex12" star within
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = red, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = yellow, col = "black")
grid.truncated_hexagonal_tiling(gp = gp)
gp <- gpar(fill = blue, col = "black")
grid.truncated_hexagonal_tiling(gp = gp, shape = "star12")
popViewport()

# Use a "star12" instead of a "convex12"
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
gp <- gpar(fill = yellow, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = blue, col = "black")
grid.truncated_hexagonal_tiling(gp = gp, shape = "star12")
popViewport()
add_borders()

```

<a name="trihexagon">Trihexagonal tiling</a>
--------------------------------------------

We can achieve one of the [uniform colorings of a trihexagonal tiling](https://en.wikipedia.org/wiki/Trihexagonal_tiling#Uniform_colorings) using the "convex6" shape with a "hex_circle" grid and rotating the shape 30 degrees.  

There are topologically equivalent tilings using the "star6", "star3", and "convex3" shapes that also provides an interesting tiling effect.

```{r}
grid.trihexagonal_tiling <- function(..., shape = "convex6", density = 1) {
    grid.pattern_regular_polygon(..., shape = shape, density = density, grid = "hex_circle",
                                 spacing = 0.2, rot = 30, angle = 0)
}
# 2 color uniform trihexagonal tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
gp <- gpar(fill = yellow, col = "black")
grid.trihexagonal_tiling(gp = gp)
popViewport()

# 'star6' trihexagonal tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
scale <- star_scale(6, 120, external = TRUE)
grid.trihexagonal_tiling(shape = "star6", scale = scale, gp = gp)
popViewport()

# 'star3' trihexagonal tiling
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
scale <- star_scale(3, 30)
grid.trihexagonal_tiling(shape = "star3", scale = scale, density=1.57, gp = gp)
popViewport()

# 'convex3' trihexagonal tiling
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
grid.trihexagonal_tiling(shape = "convex3", density=1.33, gp = gp)
popViewport()
add_borders()
```

<a name=snubtrihex>Snub trihexagonal tiling</a>
-----------------------------------------

We can achieve the one [uniform colorings of a snub (tri)hexagonal tiling](https://en.wikipedia.org/wiki/Snub_trihexagonal_tiling) using a "star6" shape and a "convex6" shape.

```{r}
grid.snub_trihexagonal <- function(..., gp_tri, gp_tri2 = gp_tri, gp_hex = gp_tri) {
    scale_star <- star_scale(6, 60 + 60, external = TRUE)
    grid.polygon(x_sq, y_sq, gp = gp_tri)
    grid.pattern_regular_polygon(shape = "star6", scale = scale_star,
                                 grid = "hex_circle",
                                 angle = 0, rot = 19, spacing = 0.2,
                                 density = 1.305, gp = gp_tri2)
    grid.pattern_regular_polygon(shape = "convex6", grid = "hex_circle",
                                 angle = 0, rot = 19 + 30, spacing = 0.2,
                                 density = scale_star * 1.305, gp = gp_hex)
}

# 3 color uniform snub square tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
gp_y <- gpar(fill = yellow, col = "black")
gp_r <- gpar(fill = red, col = "black")
gp_b <- gpar(fill = blue, col = "black")
grid.snub_trihexagonal(gp_tri = gp_b, gp_tri2 = gp_r, gp_hex = gp_y)
popViewport()

# 2 color snub trihexagonal tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.snub_trihexagonal(gp_tri = gp_y, gp_hex = gp_r)
popViewport()

# 1 color snub trihexagonal tiling
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.snub_trihexagonal(gp_tri = gp_y)
popViewport()

pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
popViewport()
add_borders()
```


<a name="truncatedtrihexagon">Truncated trihexagonal</a>
---------------------------------------------------------------------------------------

By carefully using `grid.pattern_stripe()` it is possible to achieve the [truncated trihexagonal tiling](https://en.wikipedia.org/wiki/Truncated_trihexagonal_tiling).

```{r}
# truncated trihexagonal
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = red, col = "black")
grid.pattern_stripe(grid = "hex_circle", density = 0.42, spacing = 0.3,
                    angle = 0, gp = gp)
grid.pattern_stripe(grid = "hex_circle", density = 0.42, spacing = 0.3, 
                    angle = -60, gp = gp)
grid.pattern_stripe(grid = "hex_circle", density = 0.42, spacing = 0.3, 
                    angle = 60, gp = gp)
gp <- gpar(fill = blue, col = "black")
grid.pattern_regular_polygon(shape = "convex6", grid = "hex_circle", 
                             density = 0.75, spacing = 0.3, angle = 0, gp = gp)
popViewport()

# truncated trihexagonal with 5 colors
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = green, col = NA))
gp <- gpar(fill = orange, col = "black")
grid.pattern_stripe(grid = "hex_circle", density = 0.42, spacing = 0.3, 
                    angle = 0, gp = gp)
grid.pattern_stripe(grid = "hex_circle", density = 0.42, spacing = 0.3, 
                    angle = -60, gp = gp)
grid.pattern_stripe(grid = "hex_circle", density = 0.42, spacing = 0.3, 
                    angle = 60, gp = gp)
gp <- gpar(fill = c(yellow, red, blue), col = "black")
grid.pattern_regular_polygon(shape = "convex6", grid = "hex_circle", 
                             density = 0.75, spacing = 0.3, angle = 0, gp = gp)
popViewport()
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
popViewport()
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
popViewport()
add_borders()
```

<a name="rhombitrihexagon">Rhombitrihexagonal tiling</a>
---------------------------------------------------------------------------------------

By carefully using `grid.pattern_stripe()` it is also possible to achieve the [rhombitrihexagonal tiling](https://en.wikipedia.org/wiki/Rhombitrihexagonal_tiling).  There are also variant tilings where we add in "star12" polygons.

```{r}
# rhombitrihexagonal
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = red, col = "black")
grid.pattern_stripe(grid = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = 0, gp = gp)
grid.pattern_stripe(grid = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = -60, gp = gp)
grid.pattern_stripe(grid = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = 60, gp = gp)
gp <- gpar(fill = blue, col = "black")
grid.pattern_regular_polygon(shape = "convex12", grid = "hex_circle", rot = 15,
                             density = 0.82, spacing = 0.3, angle = 0, gp = gp)
popViewport()

# rhombitrihexagonal with 5 colors
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = green, col = NA))
gp <- gpar(fill = red, col = "black")
grid.pattern_stripe(grid = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = 0, gp = gp)
gp <- gpar(fill = yellow, col = "black")
grid.pattern_stripe(grid = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = -60, gp = gp)
gp <- gpar(fill = blue, col = "black")
grid.pattern_stripe(grid = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = 60, gp = gp)
gp <- gpar(fill = orange, col = "black")
grid.pattern_regular_polygon(shape = "convex12", grid = "hex_circle", rot = 15,
                             density = 0.82, spacing = 0.3, angle = 0, gp = gp)
popViewport()

# 3.4.6.3.12* rhombitrihexagonal plus star
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = red, col = "black")
grid.pattern_stripe(grid = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = 0, gp = gp)
grid.pattern_stripe(grid = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = -60, gp = gp)
grid.pattern_stripe(grid = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = 60, gp = gp)
gp <- gpar(fill = blue, col = "black")
grid.pattern_regular_polygon(shape = "convex12", grid = "hex_circle", rot = 15,
                             density = 0.82, spacing = 0.3, angle = 0, gp = gp)
gp <- gpar(fill = green, col = "black")
scale <- star_scale(12, 30)
grid.pattern_regular_polygon(shape = "star12", grid = "hex_circle", rot = 15,
                             density = 0.82, spacing = 0.3, angle = 0, gp = gp,
                             scale = scale)
popViewport()

pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
popViewport()
add_borders()
```

<a name="star">Additional uniform tilings with star polygons</a>
---------------------------------------------------------------

Some additional [uniform tilings with star polygons](https://en.wikipedia.org/wiki/Uniform_tiling#Uniform_tilings_using_star_polygons) not shown above.

```{r}
# 12.12.4*
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
gp <- gpar(fill = c(yellow, blue), col = "black")
grid.pattern_regular_polygon(shape="convex12", rot=15, density=1.035, 
                             angle=0, gp = gp, spacing=0.3)
popViewport()

# 12.3*.12.3*
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
gp <- gpar(fill = c(yellow), col = "black")
grid.pattern_regular_polygon(shape="convex12", density=1, grid = "hex_circle",
                             angle=0, gp = gp, spacing=0.4)
popViewport()

# 4.4*.4**
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
gp <- gpar(fill = c(yellow, blue), col = "black")
gp <- gpar(fill=yellow)
scale <- star_scale(4, 30)
grid.pattern_regular_polygon(shape="star4", density=1.60, angle=0, scale=scale, 
                             rot=-9.5, spacing=0.3, gp = gp)
popViewport()

# 3.3.8*.4**.8*
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
sp <- 0.35
gp <- gpar(fill = red, col = "black")
grid.pattern_regular_polygon(shape = "square", density = 1, angle = 0, 
                             spacing = sp, gp = gp)
gp <- gpar(fill = yellow, col = "black")
scale <- star_scale(4, 60)
grid.pattern_regular_polygon(shape = "star4", density = 1.14, rot = 45, 
                             xoffset = sp / 2, yoffset = sp / 2,
                             angle = 0, scale = scale, spacing = sp, gp = gp)
gp <- gpar(fill = blue, col = "black")
scale <- star_scale(8, 15)
grid.pattern_regular_polygon(shape = "star8", density = 1.082, rot = 22.5, 
                             angle = 0, scale = 0.30, spacing = sp, gp = gp)
popViewport()
add_borders()
```

```{r}
# 3.6*.6**
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
gp <- gpar(fill = yellow, col = "black")
scale <- star_scale(6, 30)
grid.pattern_regular_polygon(shape="star6", density=1.30, angle=0, scale=scale, rot=-22.0, 
                             spacing=0.3, grid="hex", gp=gp)
popViewport()

# 4.6.4*.6
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = c(blue, red), col = "black")
scale <- star_scale(4, 120, external = TRUE)
grid.pattern_regular_polygon(shape=c("star4", "convex4"), density=c(1.2, 0.8), 
                             scale = scale, 
                             spacing = 0.2, gp = gp, angle=45)
popViewport()

# 9.3.9.3*
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
gp <- gpar(fill = blue, col = NA)
grid.pattern_stripe(spacing = 0.4, density = 0.35, angle = 0,
                    grid = "hex_circle", gp = gp, yoffset = 0.096)
gp <- gpar(fill = yellow, col = "black")
grid.pattern_regular_polygon(shape = "convex9", density = 1.01, angle = 0, 
                             grid = "hex_circle", spacing = 0.4, gp = gp)
popViewport()

# 8.4*.8.4*
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
gp <- gpar(fill = yellow, col = "black")
grid.pattern_regular_polygon(shape = c("convex8", "null"), density = 1.41, 
                             angle = 0, spacing = 0.2, gp = gp)
popViewport()
add_borders()
```

```{r}
# 18.18.3*
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = blue, col = NA))
gp <- gpar(fill = c(red, yellow), col = "black")
grid.pattern_regular_polygon(shape = "convex18", density = 1, 
                             grid = "hex_circle", angle = 0,
                             spacing = 0.2, gp = gp)
popViewport()

# Only uniform if you consider the larger squares to be four-pointed stars...
# 4.8*.4**.8*
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = blue, col = NA))
gp <- gpar(fill = c(yellow, red), col = "black")
scale <- star_scale(8, 90, external = TRUE)
grid.pattern_regular_polygon(shape = c("star8", "convex4"), scale = scale,
                             density = c(1.53, 1.2), rot = c(22.5, 0), 
                             angle = 0, spacing = 0.2, gp = gp)
popViewport()
add_borders()

<a name=non>Non-uniform tilings</a>
===================================

<a name="herringbone">Herringbone tiling</a>
--------------------------------------------

We can achieve a [herringbone tiling](https://en.wikipedia.org/wiki/Herringbone_pattern) by using `grid.pattern_weave()` and particular "twill" weaves of the subtype "n/n(1)".

```{r}
grid.herringbone_tiling <- function(..., subtype = "2/2(1)") {
    grid.pattern_weave(..., type = "twill", subtype = subtype, density = 1, 
                       spacing = 0.1, angle = 45)
}
# 1 color 2:1 herringbone 
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = yellow, col = "black")
grid.herringbone_tiling(gp = gp)
popViewport()

# 2 color 2:1 herringbone
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = yellow, col = "black")
grid.herringbone_tiling(gp = gp, fill2 = red)
popViewport()

# 1 color 3:1 herringbone
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
gp <- gpar(fill = yellow, col = "black")
grid.herringbone_tiling(gp = gp, subtype = "3/3(1)")
popViewport()

# 2 color 3:1 herringbone
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
gp <- gpar(fill = yellow, col = "black")
grid.herringbone_tiling(gp = gp, fill2 = red, subtype = "3/3(1)")
popViewport()
add_borders()
```

<a name="pythagorean">Pythagorean tiling</a>
--------------------------------------------

We can get a [Pythagorean tiling](https://en.wikipedia.org/wiki/Pythagorean_tiling) by setting a background color and rotating "convex4" shapes

```{r}
grid.pythagorean_tiling <- function(...) {
    grid.pattern_regular_polygon(..., shape = "convex4", density = 1.222, 
                                 rot = 15, spacing = 0.2, angle = -15)
}
# 1 color Pythagorean tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = yellow, col = "black")
grid.pythagorean_tiling(gp = gp)
popViewport()

# 2 color Pythagorean tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = red, col = "black")
grid.pythagorean_tiling(gp = gp)
popViewport()

# 3 color Pythagorean tiling
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = c(blue, red), col = "black")
grid.pythagorean_tiling(gp = gp)
popViewport()

# 4 color Pythagorean tiling
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = c(red, blue, green), col = "black")
grid.pythagorean_tiling(gp = gp)
popViewport()
add_borders()
```

<a name="rhombille">Rhombille tiling</a>
----------------------------------------------

We can get a [rhombille tiling](https://en.wikipedia.org/wiki/Rhombille_tiling) by using the "rhombille_rhombus" shape:

```{r}
grid.rhombille_tiling <- function(gp1, gp2 = gp1, gp3 = gp2) {
    grid.pattern_regular_polygon(shape = "rhombille_rhombus", density = 1,
                       angle = 0, rot = -120, spacing = 0.2,
                       grid = "hex", gp = gp3)
    grid.pattern_regular_polygon(shape = "rhombille_rhombus", density = 1,
                       angle = 0, rot =  120, spacing = 0.2,
                       grid = "hex", gp = gp2)
    grid.pattern_regular_polygon(shape = "rhombille_rhombus", density = 1,
                       angle = 0, rot = 0, spacing = 0.2,
                       grid = "hex", gp = gp1)
}
gp1 <- gpar(fill = yellow, col = "black")
gp2 <- gpar(fill = blue, col = "black")
gp3 <- gpar(fill = red, col = "black")
# 1 color rhombille tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.rhombille_tiling(gp1)
popViewport()
# 2 color rhombille tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.rhombille_tiling(gp1, gp2)
popViewport()
# 3 color rhombille tiling
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.rhombille_tiling(gp1, gp2, gp3)
popViewport()
add_borders()
```

<a name="tetrakis">Tetrakis square tiling</a>
---------------------------------------------

We can get a [tetrakis square tiling](https://en.wikipedia.org/wiki/Tetrakis_square_tiling) by using the "tetrakis_left" and "tetrakis_right" shapes:

```{r}
grid.tetrakis_tiling <- function(gp1, gp2 = gp1, gp3 = gp2, gp4 = gp1) {
    grid.pattern_regular_polygon(shape = "tetrakis_left", density = 1, 
                                 angle = 0, rot=0, gp = gp1, spacing = 0.25)
    grid.pattern_regular_polygon(shape = "tetrakis_left", density = 1, 
                                 angle = 0, rot=90, gp = gp4, spacing = 0.25)
    grid.pattern_regular_polygon(shape = "tetrakis_left", density = 1,
                                 angle = 0, rot=180, gp = gp1, spacing = 0.25)
    grid.pattern_regular_polygon(shape = "tetrakis_left", density = 1,
                                 angle = 0, rot=270, gp = gp4, spacing = 0.25)
    grid.pattern_regular_polygon(shape = "tetrakis_right", density = 1,
                                 angle = 0, rot=0, gp = gp2, spacing = 0.25)
    grid.pattern_regular_polygon(shape = "tetrakis_right", density = 1,
                                 angle = 0, rot=90, gp = gp3, spacing = 0.25)
    grid.pattern_regular_polygon(shape = "tetrakis_right", density = 1,
                                 angle = 0, rot=180, gp = gp2, spacing = 0.25)
    grid.pattern_regular_polygon(shape = "tetrakis_right", density = 1,
                                 angle = 0, rot=270, gp = gp3, spacing = 0.25)

}
gp1 <- gpar(fill = yellow, col = "black")
gp2 <- gpar(fill = blue, col = "black")
gp3 <- gpar(fill = red, col = "black")
gp4 <- gpar(fill = green, col = "black")
# 1 color tetrakis square tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.tetrakis_tiling(gp1)
popViewport()
# 2 color tetrakis square tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.tetrakis_tiling(gp1, gp2)
popViewport()
# 3 color tetrakis square tiling
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.tetrakis_tiling(gp1, gp2, gp3)
popViewport()
# 4 color tetrakis square tiling
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
grid.tetrakis_tiling(gp1, gp2, gp3, gp4)
popViewport()
add_borders()
```

<a name="rhombi">Additional tilings using rhombi</a>
----------------------------------------------------

A rhombi may be produced by the "star2" shape:

```{r}
# 2*.2**.2*.2**
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
sp <- 0.3
ang <- 63.5
scale <- 0.5
gpy <- gpar(fill = yellow, col = "black")
grid.pattern_regular_polygon(shape = "star2", scale = scale, angle = ang,
                             density = 1, spacing = sp, gp = gpy)
grid.pattern_regular_polygon(shape = "star2", scale = scale, angle = ang,
                             density = 1, spacing = sp, gp = gpy,
                             xoffset = 0.5 * sp)
gpr <- gpar(fill = red, col = "black")
grid.pattern_regular_polygon(shape = "star2", scale = scale, angle = ang,
                             density = 1, spacing = sp, gp = gpr,
                             xoffset = 0.25 * sp, yoffset = 0.5 * sp)
grid.pattern_regular_polygon(shape = "star2", scale = scale, angle = ang,
                             density = 1, spacing = sp, gp = gpr,
                             xoffset = 0.75 * sp, yoffset = 0.5 * sp)
popViewport()

# 4.2*.4.2**
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
dens_sq <- 0.73
scale <- star_scale(2, 60)
dens_rh <- 0.88
gpy <- gpar(fill = yellow, col = "black")
gpb <- gpar(fill = blue, col = "black")
gpr <- gpar(fill = red, col = "black")
grid.pattern_regular_polygon(shape = "convex4", scale = scale, angle = 0,
                             rot = 60,
                             density = dens_sq, spacing = sp, gp = gpb)
grid.pattern_regular_polygon(shape = "star2", scale = scale, angle = 0,
                             density = dens_rh, spacing = sp, gp = gpy,
                             rot = 45, xoffset = 0.5 * sp)
grid.pattern_regular_polygon(shape = "convex4", scale = scale, angle = 0,
                             rot = -60, yoffset = 0.5 * sp, xoffset = 0.5 * sp,
                             density = dens_sq, spacing = sp, gp = gpr)
grid.pattern_regular_polygon(shape = "star2", scale = scale, angle = 0,
                             density = dens_rh, spacing = sp, gp = gpy,
                             rot = -45, yoffset = 0.5 * sp)
popViewport()
add_borders()

```
