---
title: "Polygon Tiling Examples"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Polygon Tiling Examples}
    %\VignetteEngine{knitr::rmarkdown}
    \usepackage[utf8]{inputenc}
---

### Table of Contents

* [Triangular tiling](#triangle)
* [Square tiling](#square)
* [Hexagonal tiling](#hexagon)
* [Truncated square tiling](#truncatedsquare)
* [Truncated hexagonal tiling](#truncatedhex)
* [Trihexagonal tiling](#trihexagon)
* [Truncated trihexagonal and rhombitrihexagonal tiling](#truncatedtrihexagon)
* [Additional uniform tilings with star polygons](#star)

Several uniform regular polygon tiling patterns can be achieved by use of `grid.pattern_regular_polygon()` plus perhaps `grid.polygon()` to set a background color.  This vignette highlights several such tiling patterns.

```{r}
library("grid")
library("gridpattern")
add_borders <- function() {
    pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
    grid.rect(gp = gpar(fill = NA, col = "white", lwd = 6))
    popViewport()
    pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
    grid.rect(gp = gpar(fill = NA, col = "white", lwd = 6))
    popViewport()
    pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
    grid.rect(gp = gpar(fill = NA, col = "white", lwd = 6))
    popViewport()
    pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
    grid.rect(gp = gpar(fill = NA, col = "white", lwd = 6))
    popViewport()
}
x_sq <- c(0, 0, 1, 1)
y_sq <- c(0, 1, 1, 0)
# colorblind accessible scheme https://jfly.uni-koeln.de/color/
blue <- grDevices::rgb(0.35, 0.70, 0.90)
yellow <- grDevices::rgb(0.95, 0.90, 0.25)
red <- grDevices::rgb(0.80, 0.40, 0.00)
green <- grDevices::rgb(0.00, 0.60, 0.50)
orange <- grDevices::rgb(0.90, 0.60, 0.00)
```


<a name="triangle">Triangular tiling</a>
-----------------------------------------

When we consider the background to be a triangle fill color we can straight-forwardly
achieve three [uniform colorings of a triangular tiling](https://en.wikipedia.org/wiki/Triangular_tiling#Uniform_colorings) using the "convex3" shape with the "hex" type.

```{r}
grid.triangular_tiling <- function(...) {
    grid.pattern_regular_polygon(..., shape = "convex3", density = 1, type = "hex",
                                 spacing = 0.2, angle = 0)
}
# 1 color uniform triangular tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = yellow, col = "black")
grid.triangular_tiling(gp = gp)
popViewport()
# 2 color uniform triangular tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = red, col = "black")
grid.triangular_tiling(gp = gp)
popViewport()
# 4 color uniform triangular tiling
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = c(red, blue, green), col = "black")
grid.triangular_tiling(gp = gp)
popViewport()
add_borders()
```

<a name="square">Square tiling</a>
----------------------------------

We can achieve several [uniform colorings of a square tiling](https://en.wikipedia.org/wiki/Square_tiling#Uniform_colorings) using either the "square" or "convex4" shapes.

```{r}
# 2 color uniform square tiling (1212)
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = c(yellow, red), col = "black")
grid.pattern_regular_polygon(shape = "square", density = 1, 
                             spacing = 0.2, angle = 0, gp = gp)
popViewport()
# 2 color uniform square tiling (1122)
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = c(yellow, red), col = "black")
grid.pattern_regular_polygon(shape = "square", density = 1, type = "horizontal",
                             spacing = 0.2, angle = 0, gp = gp)
popViewport()
# 3 color uniform square tiling (1213)
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = c(red, blue), col = "black")
grid.pattern_regular_polygon(shape = "convex4", density = 1,
                             spacing = 0.2, angle = 45, gp = gp)
popViewport()
# 4 color uniform square tiling (1234)
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
gp <- gpar(fill = c(yellow, red), col = "black")
grid.pattern_regular_polygon(shape = "convex4", density = 1,
                             spacing = 0.2, angle = 45, gp = gp)
gp <- gpar(fill = c(blue, green), col = "black")
grid.pattern_regular_polygon(shape = "convex4", density = 1,
                             xoffset = 0.1, yoffset = 0.1,
                             spacing = 0.2, angle = 45, gp = gp)
popViewport()
add_borders()
```

<a name="hexagon">Hexagonal tiling</a>
--------------------------------------------

We can achieve two [uniform colorings of a hexagonal tiling](https://en.wikipedia.org/wiki/Hexagonal_tiling#Uniform_colorings) using the "convex6" shape with the "hex" type.

```{r}
grid.hexagonal_tiling <- function(...) {
    grid.pattern_regular_polygon(..., shape = "convex6", density = 1, type = "hex",
                                 spacing = 0.2, angle = 0)
}
# 1 color uniform hexagonal tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = yellow, col = "black")
grid.hexagonal_tiling(gp = gp)
popViewport()
# 3 color uniform hexagonal tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = c(yellow, red, blue), col = "black")
grid.hexagonal_tiling(gp = gp)
popViewport()
add_borders()
```

<a name=truncatedsquare>Truncated square tiling</a>
---------------------------------------------------

We can achieve the two [uniform colorings of a truncated square tiling](https://en.wikipedia.org/wiki/Truncated_square_tiling#Uniform_colorings) using the "convex8" shape rotated 22.5 degrees.  Adding in an extra (possibly alternating) "star8" shape results in a uniform tiling using star polygons.


```{r}
# 2 color uniform truncated square tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = red, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = yellow, col = "black")
grid.pattern_regular_polygon(shape = "convex8", density = 1.082, rot = 22.5, 
                             angle = 0, spacing = 0.3, gp = gp)
popViewport()
# 3 color uniform truncated square tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = blue, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = c(red, yellow), col = "black")
grid.pattern_regular_polygon(shape = "convex8", density = 1.082, rot = 22.5, 
                             angle = 0, spacing = 0.3, gp = gp)
popViewport()
# 3 color uniform truncated square tiling with star
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
gp <- gpar(fill = red, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = yellow, col = "black")
grid.pattern_regular_polygon(shape = "convex8", density = 1.082, rot = 22.5, 
                             angle = 0, spacing = 0.3, gp = gp)
gp <- gpar(fill = orange, col = "black")
grid.pattern_regular_polygon(shape = "star8", density = 1.082, rot = 22.5, 
                             angle = 0, scale = 0.54, spacing = 0.3, gp = gp)
popViewport()
# 4 color uniform truncated square tiling with an alternating star
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
gp <- gpar(fill = blue, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = c(red, yellow), col = "black")
grid.pattern_regular_polygon(shape = "convex8", density = 1.082, rot = 22.5, 
                             angle = 0, spacing = 0.3, gp = gp)
gp <- gpar(fill = orange, col = c("black"))
grid.pattern_regular_polygon(shape = c("null", "star8"), 
                             density = 1.082, rot = 22.5, 
                             angle = 0, scale = 0.54, spacing = 0.3, gp = gp)
popViewport()
add_borders()
```

<a name="truncatedhex">Truncated hexagonal tiling</a>
-----------------------------------------------------

We can achieve a [truncated hexagonal tiling](https://en.wikipedia.org/wiki/Truncated_hexagonal_tiling) using the "convex12" shape with a 15 degree rotation in a "hex_circle" type.  The related "star12" variations are fun tilings as well.

```{r}
# 2 color uniform truncated hexagonal tiling
grid.truncated_hexagonal_tiling <- function(..., shape = "convex12") {
    grid.pattern_regular_polygon(..., shape = shape, density = 1.034, spacing = 0.3,
                                 angle = 0, rot = 15, scale = 0.52, 
                                 type = "hex_circle")
}
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = red, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = yellow, col = "black")
grid.truncated_hexagonal_tiling(gp = gp)
popViewport()
# Add in a "convex12" star within
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
gp <- gpar(fill = red, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = yellow, col = "black")
grid.truncated_hexagonal_tiling(gp = gp)
gp <- gpar(fill = blue, col = "black")
grid.truncated_hexagonal_tiling(gp = gp, shape = "star12")
popViewport()
# Use a "star12" instead of a "convex12"
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
gp <- gpar(fill = yellow, col = NA)
grid.polygon(x_sq, y_sq, gp = gp)
gp <- gpar(fill = blue, col = "black")
grid.truncated_hexagonal_tiling(gp = gp, shape = "star12")
popViewport()
add_borders()

```

<a name="trihexagon">Trihexagonal tiling</a>
--------------------------------------------

We can achieve one of the [uniform colorings of a trihexagonal tiling](https://en.wikipedia.org/wiki/Trihexagonal_tiling#Uniform_colorings) using the "convex6" shape with "hex_circle" and rotating the shape 30 degrees.  

There are topologically equivalent tilings using the "star6", "star3", and "convex3" shapes that also provides an interesting tiling effect.

```{r}
grid.trihexagonal_tiling <- function(..., shape = "convex6", density = 1) {
    grid.pattern_regular_polygon(..., shape = shape, density = density, type = "hex_circle",
                                 spacing = 0.2, rot = 30, angle = 0)
}
# 2 color uniform trihexagonal tiling
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
gp <- gpar(fill = yellow, col = "black")
grid.trihexagonal_tiling(gp = gp)
popViewport()
# 'star6' trihexagonal tiling
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
grid.trihexagonal_tiling(shape = "star6", scale = 0.57, gp = gp)
popViewport()
# 'star3' trihexagonal tiling
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
grid.trihexagonal_tiling(shape = "star3", scale = 0.2, density=1.65, gp = gp)
popViewport()
# 'convex3' trihexagonal tiling
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = red, col = NA))
grid.trihexagonal_tiling(shape = "convex3", density=1.33, gp = gp)
popViewport()
add_borders()
```

<a name="truncatedtrihexagon">Truncated trihexagonal and rhombitrihexagonal tiling</a>
---------------------------------------------------------------------------------------

By carefully using `grid.pattern_stripe()` it is possible to achieve the [truncated trihexagonal tiling](https://en.wikipedia.org/wiki/Truncated_trihexagonal_tiling) and the related [rhombitrihexagonal tiling](https://en.wikipedia.org/wiki/Rhombitrihexagonal_tiling).

```{r}
# Make sure our viewport is square
pushViewport(viewport(width = unit(1, "snpc"), height = unit(1, "snpc")))
# truncated trihexagonal
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = red, col = "black")
grid.pattern_stripe(type = "hex_circle", density = 0.42, spacing = 0.3,
                    angle = 0, gp = gp)
grid.pattern_stripe(type = "hex_circle", density = 0.42, spacing = 0.3, 
                    angle = -60, gp = gp, yoffset=-0.110)
grid.pattern_stripe(type = "hex_circle", density = 0.42, spacing = 0.3, 
                    angle = 60, gp = gp, yoffset=0.068)
gp <- gpar(fill = blue, col = "black")
grid.pattern_regular_polygon(shape = "convex6", type = "hex_circle", 
                             density = 0.75, spacing = 0.3, angle = 0, gp = gp)
popViewport()
# truncated trihexagonal with 5 colors
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = green, col = NA))
gp <- gpar(fill = orange, col = "black")
grid.pattern_stripe(type = "hex_circle", density = 0.42, spacing = 0.3, 
                    angle = 0, gp = gp)
grid.pattern_stripe(type = "hex_circle", density = 0.42, spacing = 0.3, 
                    angle = -60, gp = gp, yoffset=-0.110)
grid.pattern_stripe(type = "hex_circle", density = 0.42, spacing = 0.3, 
                    angle = 60, gp = gp, yoffset=0.068)
gp <- gpar(fill = c(yellow, red, blue), col = "black")
grid.pattern_regular_polygon(shape = "convex6", type = "hex_circle", 
                             density = 0.75, spacing = 0.3, angle = 0, gp = gp)
popViewport()
# rhombitrihexagonal
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = red, col = "black")
grid.pattern_stripe(type = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = 0, gp = gp)
grid.pattern_stripe(type = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = -60, gp = gp, yoffset=-0.110)
grid.pattern_stripe(type = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = 60, gp = gp, yoffset=0.068)
gp <- gpar(fill = blue, col = "black")
grid.pattern_regular_polygon(shape = "convex12", type = "hex_circle", rot = 15,
                             density = 0.82, spacing = 0.3, angle = 0, gp = gp)
popViewport()
# rhombitrihexagonal with 5 colors
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = green, col = NA))
gp <- gpar(fill = red, col = "black")
grid.pattern_stripe(type = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = 0, gp = gp)
gp <- gpar(fill = yellow, col = "black")
grid.pattern_stripe(type = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = -60, gp = gp, yoffset=-0.110)
gp <- gpar(fill = blue, col = "black")
grid.pattern_stripe(type = "hex_circle", density = 0.25, spacing = 0.3, 
                    angle = 60, gp = gp, yoffset=0.068)
gp <- gpar(fill = orange, col = "black")
grid.pattern_regular_polygon(shape = "convex12", type = "hex_circle", rot = 15,
                             density = 0.82, spacing = 0.3, angle = 0, gp = gp)
popViewport()
add_borders()
popViewport()
```

<a name="star">Additional uniform tilings with star polygons</a>
---------------------------------------------------------------

Some additional [uniform tilings with star polygons](https://en.wikipedia.org/wiki/Uniform_tiling#Uniform_tilings_using_star_polygons) not shown above.

```{r}
# 12.12.4_{pi/3}
pushViewport(viewport(x=0.25, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = c(red, blue), col = "black")
grid.pattern_regular_polygon(shape="convex12", rot=15, density=1.04, 
                             angle=0, gp = gp, spacing=0.3)
popViewport()
# (12.3_{pi/6})^2
pushViewport(viewport(x=0.75, y=0.75, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = blue, col = NA))
gp <- gpar(fill = c(red, orange, yellow), col = "black")
grid.pattern_regular_polygon(shape="convex12", density=1, type = "hex_circle",
                             angle=0, gp = gp, spacing=0.3)
popViewport()
# (6.6_{pi/3})^2
pushViewport(viewport(x=0.25, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = red, col = "black")
grid.pattern_regular_polygon(shape="star6", density=0.86, type = "hex",
                             rot = 30, scale = 0.582,
                             angle=0, gp = gp, spacing=0.3)
popViewport()
# (4.6_{pi/6})^3
pushViewport(viewport(x=0.75, y=0.25, width=0.5, height=0.5))
grid.polygon(x_sq, y_sq, gp = gpar(fill = yellow, col = NA))
gp <- gpar(fill = red, col = "black")
grid.pattern_regular_polygon(shape="star6", density=1.0, type = "hex",
                             scale = 0.35, angle=0, gp = gp, spacing=0.3)
popViewport()
add_borders()
```
